Peaks Over Threshold for Bursty Time Series

### 2018-10-24 article_springer/article_springer.Rmd
Chapter 4 & Simulation study (still in progress)

Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution, and estimate the exponent of the tail function with established methods such as the Hill estimator. The other option is to use estimators specifically for the tail parameter of a Mittag-Leffler distribution. The first method for parameter estimation was the fractional moment estimator proposed by [@kozubowski2001]. One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates. [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge. Furthermore, they showed in a simulation study that he log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE). Due to the form of the density function there exists no closed form for the Maximum Likelihood estimator (MLE). In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization. The MLE outperforms the log-ent estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive. In figure XX one can see that both mehtods work quite well even for very low sample sizes.

```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
knitr::include_graphics("temp.pdf")
```
<!-- The QQ-estimator [@Kratz96] is closely related to  -->
<!-- the Hill estimator and fits a  -->
<!-- least squares line through the logarithms of the ordered statistics  -->
<!-- (y-axis) and the corresponding quantiles of the exponential distribution  -->
<!-- (x-axis). The reciprocal slope is returned as the estimate of the tail  -->
<!-- exponent. -->
<!-- For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the  -->
<!-- (static) QQ-estimator for the magnitudes of the solar flare data, returning  -->
<!-- a good fit to a Pareto distribution with tail parameter  -->
<!-- `r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel) -->
<!-- plots the tail exponent estimate for the largest values at cutoffs  -->
<!-- varying up to the 5th order statistic, and the region of stability at  -->
<!-- 0.8 indicates a recommended estimate. -->

@@

Since the exponential distribution is nested in the Mittag-Leffler 
family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test. Although the two models are nested, the assymptotic distribution seems no to be chi-squared since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zreo which is on the boundary of the parameter space $(0,1]$. 
<!-- Anpassen:
<!-- As an example, the threshold crossing times for the solar flare dataset -->
<!-- (Figure \ref{fig:flare-diagnostics-2}, right panel) -->
<!-- yield .  -->

@@

@@

\appendix

# Validating our inference method on simulated data

>>>>

The first method proposed for parameter estimation of the Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001]. One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates. [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge. Furthermore, they showed in a simulation study that he log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE). Due to the form of the density function there exists no closed form for the Maximum Likelihood estimator (MLE). In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization. The MLE outperforms the log-ent estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive. In figure XX one can see that both mehtods work quite well even for very low sample sizes.    
Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution. Of course, one can also use established tail exponent estimators such as the Hill estimator. However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentionded by [@kozubowski2001]. Addtionally they need a specification of a tuning parameter.

In XX we plotted a Hill plot for differet k's where .....

```{r pressure, echo=FALSE, fig.cap="MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
knitr::include_graphics("MSE_n25_100_200.pdf")
```
<!-- The QQ-estimator [@Kratz96] is closely related to  -->
<!-- the Hill estimator and fits a  -->
<!-- least squares line through the logarithms of the ordered statistics  -->
<!-- (y-axis) and the corresponding quantiles of the exponential distribution  -->
<!-- (x-axis). The reciprocal slope is returned as the estimate of the tail  -->
<!-- exponent. -->
<!-- For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the  -->
<!-- (static) QQ-estimator for the magnitudes of the solar flare data, returning  -->
<!-- a good fit to a Pareto distribution with tail parameter  -->
<!-- `r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel) -->
<!-- plots the tail exponent estimate for the largest values at cutoffs  -->
<!-- varying up to the 5th order statistic, and the region of stability at  -->
<!-- 0.8 indicates a recommended estimate. -->

@@

Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test. Although the two models are nested, the assymptotic distribution seems not to be $\chi^2_1$ since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero which is on the boundary of the parameter space $(0,1]$.

```{r LRT power, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
knitr::include_graphics("Plots_LRT_boot.pdf")
```

```{r LRT type one error, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
knitr::include_graphics("Plots_LRT_boot_typeOneError.pdf")
```

<!-- Anpassen:
<!-- As an example, the threshold crossing times for the solar flare dataset -->
<!-- (Figure \ref{fig:flare-diagnostics-2}, right panel) -->
<!-- yield .  -->

@@

# Simulation study

@@
